### 2010-11-11 resume_cv/cv.tex
Added my masters degree to my CV
Some updates to my cv from comments from Sabrina

\section{Research Interests}
%
Particle swarm optimization, natural language processing, Latent Dirichlet
Allocation, Bayesian machine learning, Markov decision processes, value
iteration

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Minors in Physics and Mathematics
        \item Graduated summa cum laude (GPA 4.0) and with University honors
        \item Thesis Topic: \emph{Speculative Evaluation in Particle Swarm
            Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

{\textbf{Brigham Young University}}, Provo, Utah USA
\begin{outerlist}
\item[] \textit{Teaching Assistant}%
	\hfill \textbf{May 2010 to June 2010}
\begin{innerlist}
\item CS 470: Introduction to Artificial Intelligence.  Tutored students,
  graded homework and reports, and helped create new curriculum for the class.
\item CS 677: Bayesian Inference.  Tutored students and graded homework and
  reports.
\end{innerlist}

\item[] \textit{Undergraduate Researcher}%
        \hfill \textbf{December 2007 to April 2010}
\begin{innerlist}
\item Worked in the Applied Machine Learning Lab in the Computer Science
  Department under Dr. Kevin Seppi.
\item Reviewed papers for the International Conference on Machine Learning 2009.
\item Research topics included particle swarm optimization and Markov decision
  processes.
\end{innerlist}
\end{outerlist}

@@

\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.  Official blog post about
  the project can be found at:
  http://google-tmads.blogspot.com/2010/01/track-cost-per-call-data-through-google.html.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}

@@

\section{Publications} \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  In: \emph{Parallel Problem
	  Solving in Nature, 2010}.

>>>>

\section{Research Interests}
%
Natural language processing, latent Dirichlet allocation, topic modeling,
Bayesian machine learning, particle swarm optimization

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] M.S.,
		Computer Science, April 2011 (anticipated)
        \begin{innerlist}
		\item Thesis Topic: \emph{Information discovery in large corpora
		  through topic modeling}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Graduated summa cum laude (GPA 4.0) and with University honors
        \item Minors in Physics and Mathematics
        \item Honors Thesis Topic: \emph{Speculative Evaluation in Particle
		  Swarm Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

{\textbf{Brigham Young University}}, Provo, Utah USA
\begin{outerlist}
\item[] \textit{Teaching Assistant}%
	\hfill \textbf{May 2010 to June 2010}
\begin{innerlist}
\item CS 470: Introduction to Artificial Intelligence.  Helped create new
  curriculum for the class, tutored students, and graded homework and reports.
\item CS 677: Bayesian Inference.  Tutored students and graded homework and
  reports.
\end{innerlist}

\item[] \textit{Undergraduate Researcher}%
        \hfill \textbf{December 2007 to April 2010}
\begin{innerlist}
\item Worked in the Applied Machine Learning Lab in the Computer Science
  Department under Dr. Kevin Seppi.
\item Research topics included particle swarm optimization and Markov decision
  processes.
\item Reviewed papers for the International Conference on Machine Learning 2009.
\end{innerlist}
\end{outerlist}

@@

\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.  Official blog post about
  the project can be found at:
  http://google-tvads.blogspot.com/2010/01/track-cost-per-call-data-through-google.html.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}

@@

\section{Publications} \begin{bibsection}
	\item M. Gardner, J. Lutes, J. Lund, J. Hansen, D. Walker, E. Ringger, K.
	  Seppi. The Topic Browser: An Interactive Tool for Browsing Topic Models.
	  To appear in the Challenges of Data Visualization workshop at Neural
	  Information Processing Systems 2010.

	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  In: \emph{Parallel Problem
	  Solving in Nature, 2010}.
